---
title: "scribe"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{scribe}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(scribe)
```

The `{scribe}` package provides a means of defining command line argument inputs for use with the [Rscript](https://search.r-project.org/R/refmans/utils/html/Rscript.html) utility.
Users will primarily use the `command_args()` function to capture the command line arguments and initialize a `scribeCommandArgs` object.
A `scribeCommandArgs` is a [**Reference Class**](https://search.r-project.org/R/refmans/methods/html/refClass.html) object with methods to configure how to parse these arguments for use within **R**.

Let's look at to use the `{scribe}` class first.
Our goal is to wrap a simple function to generate a sequence of integers or letters.
Here we build out a `scribeCommandArgs` object, add a couple of arguments with the `$add_argument()` method, then parse into a named list with `$parse()`.

```{r}
ca <- command_args(c("-n", "5", "--method", "numbers"))
ca$add_argument("-n", default = 1L)
ca$add_argument("--method", default = "letters")
args <- ca$parse()

out <- seq_len(args$n)

method <- match.arg(args$method, c("letters", "numbers"))
if (method == "letters") {
  out <- letters[out]
}

out
```

In the example above we specify what the command line arguments are within `command_args()`.
The intended utility of this is to capture these arguments when passe within an `Rscript` file.
Below is the same structure, but as we would expect from within a script intended to be called from a command line.
`command_args()` will grab whatever command line arguments are passed to the script.

```R
#!/usr/bin/env Rscript
# filename: seq_len.R

library(scribe)
ca <- command_args()
ca$add_argument("-n", default = 1L)
ca$add_argument("--method", default = "letters")
args <- ca$parse()

out <- seq_len(args$n)

method <- match.arg(args$method, c("letters", "numbers"))
if (method == "letters") {
  out <- letters[out]
}

out
```

```
seq_len.R -n 3 
#> [1] "a" "b" "c"
```

```
seq_len.R -n 3 --method numbers
#> [1] 1 2 3
```

One way I like to use `{scribe}` is by passing the values directly to another function via `do.call()`.

Two examples provided that find a specified dataset and then perform something to it.
Were I to use this personally, I would probably pass a file path and use a read function first, rather than the `get()` function.

```{r}
my_summary <- function(data, levels = 7, sig_figs = 3, q_type = 7) {
  data <- get(data, mode = "list")
  stopifnot(is.data.frame(data))
  summary(data, maxsum = levels, digits = sig_figs, quantile.type = q_type)
}

my_model <- function(data, correlation = FALSE) {
  data <- get(data, mode = "list")
  stopifnot(is.data.frame(data))
  form <- stats::DF2formula(data)
  mod <- stats::lm(form, data)
  summary(mod, correlation = correlation)
}
```


```{r}
ca <- command_args(string = "CO2 --levels 3 --sig-figs 2 --q-type 3")
ca$add_description("Summarise a dataset")
ca$add_argument(
  "data",
  info = "Name of the dataset to find"
)
ca$add_argument(
  "--levels",
  default = 7L,
  info = "Maximum number of levels shown for factors"
)
ca$add_argument(
  "--sig-figs",
  default = 3L,
  info = "Number of significant figures"
)
ca$add_argument(
  "--q-type",
  default = 7L,
  info = "Quantile type"
)
args <- ca$parse()
do.call(my_summary, args)
```

```{r}
ca <- command_args(string = "attitude --correlation")
ca$add_argument(
  "data",
  info = "Name of the dataset to find"
)
ca$add_argument(
  "--correlation",
  action = "flag",
  info = "When set, prints the correlation matrix of estimated parameters"
)
args <- ca$parse()
do.call(my_model, args)
```
